---
title: "Model checks"
author: "Chris Hoover"
date: "March 25, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(deSolve)
require(rootSolve)
require(coda)
require(viridis)
require(tidyverse)

source("../Models/initial_parameters.R")
source("../Models/model_helper_functions.R")
source("../Models/r0_functions.R")
source("../Models/models.R")

load("../Models/trans_pars_fit.Rdata")
load("../Models/fit_pars.Rdata")

```

# Initial model simulations  
## $R_0$ Check  

First estimate $R_0$ from models with increasing complexity, basically to make sure no typos or anything in the more complex functions. 

```{r r0_init}
fit_pars_no_pred <- fit_pars
fit_pars_no_pred["mu_P"] <- fit_pars["f_P"]

r0.Base(fit_pars_no_pred)
r0.pred(fit_pars_no_pred)
r0.Ag(parameters = fit_pars_no_pred)


r0.pred(fit_pars)
r0.Ag(parameters = fit_pars)

```

## Equilibrium check  
Now check that the models' equilibria are the same

```{r state_vars_check}
#Base model
base.start = c(S = 40*area,
               E = 0,
               I = 0,
               W = 2)

base_eq <- runsteady(y = base.start, func = base_mod, parms = fit_pars)$y

base_eq

#Base model with predators added
base_pred.start = c(S = 40*area,
                    E = 0,
                    I = 0,
                    W = 2,
                    P = 0)

pred_eq <- runsteady(y = base_pred.start, func = pred_mod, parms = fit_pars)$y

pred_eq

#full agrochem model
agro_eq <- runsteady(y = base_pred.start, func = agrochem_mod, parms = fit_pars)$y

agro_eq

#Base model with predators, with predators added
pred.start = c(S = 40*area,
             E = 0,
             I = 0,
             W = 2,
             P = 0.1*area)

pred_eq_add_pred <- runsteady(y = pred.start, func = agrochem_mod, parms = fit_pars)$y

pred_eq_add_pred

agro_eq_add_pred <- runsteady(y = pred.start, func = pred_mod, parms = fit_pars)$y

agro_eq_add_pred

```


## $R_0$ and dynamics check  
Ensure that equilibrium worm burden is in qualitative agreement with estimates of $R_0$ (i.e. not getting rampant infection when $R_0<1$)
```{r comp_r0_w, cache = T}
test_pars <- fit_pars_no_pred

test_r0s <- numeric()
test_ws <- numeric()

pred_r0s <- numeric()
pred_ws <- numeric()

base_r0s <- numeric()
base_ws <- numeric()

for(i in seq(1, 10, 0.1)){
  test_pars["beta"] <- fit_pars["beta"]/i
  test_pars["lambda"] <- fit_pars["lambda"]/i

  test_r0s[i*10-9] <- r0.Ag(parameters = test_pars)[3]
  test_ws[i*10-9] <- runsteady(y = pred.start, func = agrochem_mod, parms = test_pars)$y["W"]

  pred_r0s[i*10-9] <- r0.pred(parameters = test_pars)[3]
  pred_ws[i*10-9] <- runsteady(y = pred.start, func = pred_mod, parms = test_pars)$y["W"]
  
  base_r0s[i*10-9] <- r0.Base(parameters = test_pars)[3]
  base_ws[i*10-9] <- runsteady(y = base.start, func = base_mod, parms = test_pars)$y["W"]
  
  #print(i*10-9)
}

plot(base_r0s, base_ws, 
     xlab = "R0", ylab = "equilibrium worm burden", main = "base model")

plot(pred_r0s, pred_ws, 
     xlab = "R0", ylab = "equilibrium worm burden", main = "pred model")

plot(test_r0s, test_ws, 
     xlab = "R0", ylab = "equilibrium worm burden", main = "agrochem model")


```

Looks good. Since $R_0$ doesn't consider the mating function, it make sense that $R_0$ has to be slightly above 1 for infection to occur. 

## Check that MDA model with agrochemical influence responds the same as non-MDA model in the absence of MDA  
```{r mda_mod_comp}
sim_time <- seq(0,365*50, 5)
  
coverage = fit_pars["cvrg"]

base_mda.start = c(S = 40*area,
                   E = 0,
                   I = 0,
                   Wt = 2*coverage,
                   Wu = 2*(1-coverage),
                   P = 0)

#Run mda model and non-mda models in absence of predaotrs
  #Sim MDA model without MDA
  no_mda_sim_mda_model <- data.frame(ode(base_mda.start, sim_time, agrochem_mda_mod,  
                                         fit_pars)) %>% 
    mutate(N = S + E + I,
           W = Wt.cvrg*coverage + Wu.cvrg * (1-coverage))
  
  no_mda_sim_mda_model %>% ggplot(aes(x = time, y = W)) +
      geom_line(size = 1.2, col = "purple") +
      theme_classic()
  
  #Sim non MDA model (w/o MDA, obviously)
  no_mda_sim_base_model <- data.frame(ode(base_pred.start, sim_time, agrochem_mod,  
                                         fit_pars)) %>% 
    mutate(N = S + E + I)
  
  no_mda_sim_base_model %>% ggplot(aes(x = time, y = W)) +
      geom_line(size = 1.2, col = "purple") +
      theme_classic()

  no_mda_sim_mda_model$W[dim(no_mda_sim_mda_model)[1]]
  no_mda_sim_base_model$W[dim(no_mda_sim_base_model)[1]]
  
#Run mda model and non-mda models with predators
base_pred_mda.start = c(S = 40*area,
                        E = 0,
                        I = 0,
                        Wt = 2*coverage,
                        Wu = 2*(1-coverage),
                        P = 0.1*area)

  #Sim MDA model without MDA
  no_mda_sim_mda_model_preds <- data.frame(ode(base_pred_mda.start, sim_time, agrochem_mda_mod,  
                                               fit_pars)) %>% 
    mutate(N = S + E + I,
           W = Wt.cvrg*coverage + Wu.cvrg * (1-coverage))
  
  no_mda_sim_mda_model_preds %>% ggplot(aes(x = time, y = W)) +
      geom_line(size = 1.2, col = "purple") +
      theme_classic()
  
  #Sim non MDA model (w/o MDA, obviously)
  no_mda_sim_base_model_preds <- data.frame(ode(pred.start, sim_time, agrochem_mod,  
                                                fit_pars)) %>% 
    mutate(N = S + E + I)
  
  no_mda_sim_base_model_preds %>% ggplot(aes(x = time, y = W)) +
      geom_line(size = 1.2, col = "purple") +
      theme_classic()
  
  no_mda_sim_mda_model_preds$W[dim(no_mda_sim_mda_model_preds)[1]]
  no_mda_sim_base_model_preds$W[dim(no_mda_sim_base_model_preds)[1]]

```

## That checks out, now let's simulate MDA and make sure the model responds as expected  
```{r sim_mda_mod}
#Events data frame containing timepoints at which MDA occurs
mda_years = 20

  mdas <- data.frame(var = rep('Wt.cvrg', mda_years),
                     time = 365*c(1:mda_years)+3650, #Start MDA after 10 years
                     value = rep(0.06, mda_years),     #94% efficacy
                     method = rep('mult', mda_years))

  
#Sim MDA model with annual MDA for mda_years
  mda_sim_mda_eq <- runsteady(y = base_mda.start, func = agrochem_mda_mod, parms = fit_pars)$y
  
  sim_mda_model <- data.frame(ode(mda_sim_mda_eq, sim_time, agrochem_mda_mod,  
                                         fit_pars, events = list(data = mdas))) %>% 
    mutate(W = Wt.cvrg*coverage + Wu.cvrg * (1-coverage))
  
  sim_mda_model %>% gather("Treatment group","Burden", Wt.cvrg, Wu.cvrg, W) %>% 
    ggplot(aes(x = time, y = Burden, lty = `Treatment group`)) +
      geom_line(size = 1.2, col = "purple") +
      theme_classic()

#Sim MDA model with annual MDA for mda_years and presence of predators
  mda_pred_sim_mda_eq <- runsteady(y = base_pred_mda.start, func = agrochem_mda_mod, parms = fit_pars)$y
  
  sim_mda_pred_model <- data.frame(ode(mda_pred_sim_mda_eq, sim_time, agrochem_mda_mod,  
                                         fit_pars, events = list(data = mdas))) %>% 
    mutate(W = Wt.cvrg*coverage + Wu.cvrg * (1-coverage))
  
  sim_mda_pred_model %>% gather("Treatment group","Burden", Wt.cvrg, Wu.cvrg, W) %>% 
    ggplot(aes(x = time, y = Burden, lty = `Treatment group`)) +
      geom_line(size = 1.2, col = "purple") +
      theme_classic()
    
```

