---
title: "d-r-sim"
author: "Chris Hoover"
date: "March 3, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warnings = FALSE, message = FALSE)
library(LW1949)
library(drc)
library(rootSolve)
```

Trying to determine how best to reproduce a dose-response function when provided with LC parameters and a slope function generated using the method of Litchfield and Wilcoxon which fits a linear response to log10(dose) -- probit(response) data.  

First generate data and fit d-r response using the `LW1949` package  
```{r generate_data}
dr <- 
  dataprep(dose = seq(0, 45, 5),
           nfx = c(0, 0, 2, 4, 5, 5, 7, 9, 10, 10),
           ntot = rep(10,10))

intslope <- fitLWauto(dr)

fLW <- LWestimate(intslope, dr)
```

Plot the linear model fit to transformed data  
```{r plot_linear}
plotDELP(dr)
  predLinesLP(fLW)
```

Plot the fit to the untransformed data  
```{r}
plotDE(dr)
  predLines(fLW)

```

Get estimates of $LC_{10}$, $LC_{25}$, $LC_{50}$, $LC_{90}$ and plot. Ideally will be able to reproduce the d-r function from only the $LC_{50}$ and $slp$ parameters  
```{r}
pars <- as.data.frame(predlinear(c(10, 25, 50, 90), fLW))
  pars$log10_ED <- log10(pars$ED)
  pars$probit <- qnorm(pars$pct/100)
  
lc50 <- predlinear(50, fLW)
slp <- fLW$LWest["S"]
    
plot(pars[,2], pars[,1], pch = 16, cex = 1.2, xlim = c(0,45), ylim = c(0,100),
     xlab = "Dose", ylab = "pct affected")
  predLines(fLW)

```

Can we reproduce the D-R function with uncertainty from $LC_{10}$, $LC_{25}$, $LC_{50}$, $LC_{90}$ and CI of $LC_{50}$?  
```{r}
plot(log10(pars[,2]), qnorm(pars[,1]/100), pch = 16, cex = 1.2, xlim = c(0,2), ylim = c(-2,2),
     xlab = "log10 Dose", ylab = "probit pct affected")
  segments(y0 = qnorm(0.5), y1 = qnorm(0.5),
           x0 = log10(pars$lower[pars$pct == 50]), x1 = log10(pars$upper[pars$pct == 50]))
  predLinesLP(fLW)

#Fit linear model to the LC values provided  
lc_mod <- lm(probit ~ log10_ED, data = pars)  

#Plot results including uncertainty of LC  
d_fx <- function(d, s, lc50){
  pnorm(s * log10(d/lc50))  
}  

lines(log10(c(0:100)), qnorm(d_fx(d = c(0:100), s = coef(lc_mod)[2], lc50 = lc50[2])), 
      lty = 3, col = 4, lwd = 2) 
lines(log10(c(0:100)), qnorm(d_fx(d = c(0:100), s = coef(lc_mod)[2], lc50 = lc50[3])), 
      lty = 3, col = 4, lwd = 2)  
lines(log10(c(0:100)), qnorm(d_fx(d = c(0:100), s = coef(lc_mod)[2], lc50 = lc50[4])), 
      lty = 3, col = 4, lwd = 2)  

#What if we sample from lc50 range?
lc50_se <- log10(lc50[4]/lc50[2]) / 1.96

d_fx_uncertainty <- function(d, s, lc50, se){
  lc_use = 10^(rnorm(1, log10(lc50), se))
  pnorm(s * log10(d/lc_use))  
} 

set.seed(43093)
points(log10(c(0:100)), qnorm(sapply(c(0:100), d_fx_uncertainty, s = coef(lc_mod)[2], lc50 = lc50[2], se = lc50_se)),
       pch = 5, col = 4, cex = 0.5)
```

Doesn't do a perfect job of reproducing uncertainty, but let's see what else we can do  

Let's see what we can do given just the $LC_{50}$ and $slp$  
```{r}
lc50 <- predlinear(50, fLW)

slp <- fLW$LWest["S"]

lc84 <- predlinear(84, fLW)
lc16 <- predlinear(16, fLW)

slp_man <- (lc84[2]/lc50[2] + lc50[2]/lc16[2])/2
#Estimate intercept of the linear model using slope as true linear slope and lc50 as a reference point
intercept = qnorm(.5) - slp*log10(lc50[2])

#d-r function using the estimated intercept and slope
dr_fx <- function(d, s, lc50){
    r = pnorm(s * log10(d/lc50))
    r
  }

plot(pars[,2], pars[,1], pch = 16, cex = 1.2, xlim = c(0,45), ylim = c(0,100),
     xlab = "Dose", ylab = "pct affected")
  points(dr$dose, (dr$nfx/dr$ntot)*100, pch = 17, col = 2)
  predLines(fLW)
  
  lines(c(0:45), dr_fx(c(0:45), s = 2*slp, lc50 = lc50[2])*100, lty = 2, col = 4)
```

We can estimate the slope of the underlying linear model, $b_1$, given the slope parameter, $S$ using some algebra:
\begin{align}
S & = \frac{\frac{LC_{84}}{LC_{50}}+\frac{LC_{50}}{LC_{16}}}{2} \\
0 & = 2*S*LC_{50}LC_{16}-LC_{84}LC_{16}-LC_{50}^2 \\ 
\intertext{We also know:}
b_1 & =\frac{probit(0.84)-probit(0.5)}{log_{10}(LC_{84})-log_{10}(LC_{50})} \\
b_1 & =\frac{probit(0.5)-probit(0.16)}{log_{10}(LC_{0.5})-log_{10}(LC_{0.16})} \\
\intertext{Solving for $LC_{84}$:}
LC_{84} & =LC_{50}10^{\frac{probit(0.84)}{b_1}} \\ 
\intertext{Solving for $LC_{16}$:}
LC_{16} & =\frac{LC_{50}}{10^{\frac{-probit(0.16)}{b_1}}} \\ 
\intertext{Substituting for $LC_{84}$ and $LC_{16}$ we have:}
0 & = 2*S*LC_{50}\frac{LC_{50}}{10^{\frac{-probit(0.16)}{b_1}}}-LC_{50}10^{\frac{probit(0.84)}{b_1}}\frac{LC_{50}}{10^{\frac{-probit(0.16)}{b_1}}}-LC_{50}^2 \\
\intertext{Dividing both sides by $LC_{50}^2$ we get:}
0 & = \frac{2S}{10^{\frac{-probit(0.16)}{b_1}}}-\frac{10^{\frac{probit(0.84)}{b_1}}}{10^{\frac{-probit(0.16)}{b_1}}}-1 \\
\intertext{We can then estimate $b_1$ given $S$ by solving the above equation}
\end{align}  

```{r}
get_b1 <- function(lc50, slp){
  uniroot.all(f = function(b1){2*slp*lc50*(lc50 / 10^(-qnorm(.16)/b1)) - (10^(qnorm(.84)/b1) * lc50)*(lc50 / 10^(-qnorm(.16)/b1)) - lc50^2}, interval = c(0, slp*10), n = 1e6)
}

get_b1(lc50 = 19.21364, slp = 1.920837)

intslope[2]
```

