---
title: "R0q_Sensitivity"
author: "Chris Hoover"
date: "January 27, 2018"
output: pdf_document
---

#Sensitivity analysis of agrochemical effects on schistosomiasis transmission measured by $R_0$ and implications for worm burden and disease

Approach here is to:
1) sample from feasible parameter ranges for each agrochemical sensitive parameter
2) estimate R0 using that set of parameters
3) run the model to equilibrium using that set of parameters
  a) record mean worm burden estimate
  b) record individual probability of having some threshold worm burden, W, corresponding to heavy and probably symptomatic infection; need to find a literature estimate for this value of W
  
  
```{r load_data, echo = FALSE}
load('~/RemaisWork/Schisto/R Codes/ag_schist/Review_models/Savio/Atrazine/atr5000sims_pars_2017-12-12.Rdata')
load('~/RemaisWork/Schisto/R Codes/ag_schist/Review_models/Savio/Butralin/but5000sims_pars_2017-12-12.Rdata')
load('~/RemaisWork/Schisto/R Codes/ag_schist/Review_models/Savio/Chlorpyrifos/ch5000sims_pars_2017-11-29.Rdata')
load('~/RemaisWork/Schisto/R Codes/ag_schist/Review_models/Savio/Glyphosate/gly5000sims_pars_2017-12-12.Rdata')
load('~/RemaisWork/Schisto/R Codes/ag_schist/Review_models/Savio/Malathion/mal5000sims_pars_2017-12-12.Rdata')
load('~/RemaisWork/Schisto/R Codes/ag_schist/Review_models/Savio/Profenofos/pr5000sims_pars_2017-12-12.Rdata')

```

```{r}

```

